A nice acyclic matching on the nerve of the partition lattice

### 2018-12-22 paper3/equivariant.tex
refs in paper3

By Remark \ref{card} the cardinality of $C_n$ is $(n-1)!$ which equals the cardinality of $S_1\times S_{n-1}$. Hence the action is free.
\end{proof}
Let $G\subset S_1\times S_{n-1}$ be an arbitrary subgroup.
\begin{rem}
The cardinality of $C_n/G$ is the index of $G$ in $S_1\times S_{n-1}$.
\end{rem}
\begin{proof}
Apply Lemma \ref{freetrans}.
\end{proof}
Now Theorem \ref{rdthm} follows as a corollary. We can either apply Corollary \ref{moeglichkeit1} or Corollary \ref{moeglichkeit2}.
\begin{cor}
The topological space $\Delta(\overline{\Pi}_n)/G$ is homotopy equivalent to a wedge of spheres of dimension $n-3$. The number of spheres is the index of $G$ in $S_1\times S_{n-1}$.
\end{cor}
\section*{Acknowledgments}
The author would like to thank Dmitry N. Kozlov for this interesting problem, Ragnar Freij and Giacomo d'Antonio for the helpful discussions.
\bibliographystyle{model1-num-names}
\begin{thebibliography}{00}
\bibitem{arone}
G. Arone, \textit{A branching rule for partition complexes}, \texttt{arXiv:1508.05086v1 [math.AT]} (2015).
\bibitem{donau2}
R. Donau, \textit{On a quotient topology of the partition lattice with forbidden block sizes}, Topology and its Applications \textbf{159} (8) (2012), pp. 2052-2057.
\bibitem{donau}
R. Donau, \textit{Quotients of the order complex $\Delta(\overline{\Pi}_n)$ by subgroups of the Young subgroup $S_1\times S_{n-1}$}, Topology and its Applications \textbf{157} (16) (2010), pp. 2476-2479.
\bibitem{torsion}
R. Donau, \textit{Quotients of the topology of the partition lattice which are not homotopy equivalent to wedges of spheres}, \texttt{arXiv:1202.4368v2 [math.AT]} (2012).
\bibitem{forman}
R. Forman, \textit{Morse theory for cell complexes}, Adv. Math. \textbf{134} (1) (1998), pp. 90-145.
\bibitem{freij}
R. Freij, \textit{Equivariant discrete Morse theory}, Discrete Mathematics \textbf{309} (12) (2009), pp. 3821-3829.
\bibitem{hatcher}
A. Hatcher, \textit{Algebraic Topology}, Cambridge University Press, 2008.
\bibitem{clmap}
D.N. Kozlov, \textit{Closure maps on regular trisps}, Topology and its Applications \textbf{156} (15) (2009), pp. 2491-2495.
\bibitem{buch}
D. Kozlov, \textit{Combinatorial Algebraic Topology}, Algorithms and Computation in Mathematics \textbf{21}, Springer-Verlag Berlin Heidelberg, 2008.
\end{thebibliography}
\end{document}

>>>>

By Remark \ref{card} the cardinality of $C_n$ is $(n-1)!$ which equals the cardinality of $S_1\times S_{n-1}$. Hence the action is free.
\end{proof}
Let $G\subset S_1\times S_{n-1}$ be an arbitrary subgroup.
\begin{rem}
The cardinality of $C_n/G$ is the index of $G$ in $S_1\times S_{n-1}$.
\end{rem}
\begin{proof}
Apply Lemma \ref{freetrans}.
\end{proof}
Now Theorem \ref{rdthm} follows as a corollary. We can either apply Corollary \ref{moeglichkeit1} or Corollary \ref{moeglichkeit2}.
\begin{cor}
The topological space $\Delta(\overline{\Pi}_n)/G$ is homotopy equivalent to a wedge of spheres of dimension $n-3$. The number of spheres is the index of $G$ in $S_1\times S_{n-1}$.
\end{cor}
\section*{Acknowledgments}
The author would like to thank Dmitry N. Kozlov for this interesting problem, Ragnar Freij and Giacomo d'Antonio for the helpful discussions.
\bibliographystyle{model1-num-names}
\begin{thebibliography}{00}
\bibitem{arone}
G. Arone, \textit{A branching rule for partition complexes}, \texttt{arXiv:1508.05086v1 [math.AT]} (2015).
\bibitem{donau2}
R. Donau, \textit{On a quotient topology of the partition lattice with forbidden block sizes}, Topology and its Applications \textbf{159} (8) (2012), pp. 2052-2057.
\bibitem{donau}
R. Donau, \textit{Quotients of the order complex $\Delta(\overline{\Pi}_n)$ by subgroups of the Young subgroup $S_1\times S_{n-1}$}, Topology and its Applications \textbf{157} (16) (2010), pp. 2476-2479.
\bibitem{torsion}
R. Donau, \textit{Quotients of the topology of the partition lattice which are not homotopy equivalent to wedges of spheres}, \texttt{arXiv:1202.4368 [math.AT]} (2012).
\bibitem{forman}
R. Forman, \textit{Morse theory for cell complexes}, Adv. Math. \textbf{134} (1) (1998), pp. 90-145.
\bibitem{freij}
R. Freij, \textit{Equivariant discrete Morse theory}, Discrete Mathematics \textbf{309} (12) (2009), pp. 3821-3829.
\bibitem{hatcher}
A. Hatcher, \textit{Algebraic Topology}, Cambridge University Press, 2008.
\bibitem{clmap}
D.N. Kozlov, \textit{Closure maps on regular trisps}, Topology and its Applications \textbf{156} (15) (2009), pp. 2491-2495.
\bibitem{buch}
D. Kozlov, \textit{Combinatorial Algebraic Topology}, Algorithms and Computation in Mathematics \textbf{21}, Springer-Verlag Berlin Heidelberg, 2008.
\bibitem{wachs}
M.L. Wachs, \textit{On the (co)homology of the partition lattice and the free Lie algebra}, Discrete Mathematics \textbf{193} (1-3) (1998), pp. 287-319.
\end{thebibliography}
\end{document}
